---
title: "Estimating Underwater Light Regime under Spatially Heterogeneous Sea Ice in the Arctic"
subtitle: "GreenEdge Legacy meeting"
author: "P. Massicotte, G. Bécu, S. Lambert-Girard, E. Leymarie and M. Babin"
date: "2019-11-06 (Nice, France)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [xaringan-themer.css, styles.css]
    self_contained: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  out.width = "100%",
  fig.align = "center",
  fig.width = 8,
  fig.asp = 0.618, # 1 / phi
  fig.show = "hold",
  dev = "svg",
  message = FALSE,
  warning = FALSE,
  echo = FALSE
)

library(tidyverse)
library(ggpmthemes)
library(fontawesome)
library(knitr)
library(kableExtra)

theme_set(theme_exo(base_size = 12))
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
duo(
  code_font_family = "Fira Code",
  code_font_url = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css",
  text_font_google = google_font("Questrial"),
  inverse_background_color = "#ABB7B7",
  inverse_text_color = "#3c3c3c",
  inverse_header_color = "#3c3c3c", 
  background_color = "#3c3c3c", 
  header_color = "#B2CCE5", 
  title_slide_text_color = "#3c3c3c",
  title_slide_background_color = "#ABB7B7"
  # Yanone Kaffeesatz
)
```

# Outlines

1. Challenges in estimating the vertical distribution of underwater light in ice-infested regions of the Arctic ocean.

2. A new method to estimate $K_d$ under sea ice covered in melt ponds.

3. 3D Monte Carlo numerical simulations of radiative transfer.

4. Results

---

class: my-one-page-font, inverse, center, middle

# The vertical distribution of underwater light in the Arctic ocean

---

# The importance of underwater light

- Important driver of many aquatic processes:
  - primary production
  - photodegradation of organic matter.

- An adequate description of the underwater light regime is mandatory to understand energy fluxes in aquatic ecosystems.

---

# The importance of underwater light

- Attenuation coefficient, $K_d$, is one of the most commonly used apparent optical properties (AOP) of seawater.

  - A good estimation of this parameter is important for measuring or modelling primary production

---

# Vertical light distribution in open water

Assuming an optically homogeneous water column, the decrease of light with increasing depth can be modeled as follow:

Equation here: 

---

# Vertical light distribution in open water

Show an example

---

# Vertical light distribution in ice-covered water

In ice-covered regions, estimating the vertical distribution of light is much more challenging.

Figure with meltpond (maybe Frey?)

---

# Vertical light distribution in ice-covered water

Discrete light measurement do not capture the variability induced by sea ice features.

--

1. Local measurements: C-OPS

--

2. ROV and SUITE

--

3. why3

---

# The main objective

Propose **a new method to estimate average irradiance over large spatially heterogeneous area** as it would be seen by drifting phytoplankton.

Add the notation of $K_d$ with the bar (average Kd)

---

# Upward radiance: A New Hope

- Why not use $K_{Lu}$?

- Graph showing that Ed and Lu (thus Ked and KLu) are very similar.

Fig. 3 + Fig. 4 with normalized vertical profiles

---

# What we did

1. Used both *in-situ* and Monte-Carlo simulation to prove that (KLu) can be used as a proxy to estimate MEAN Ed(z) in the water column.

---

class: my-one-page-font, inverse, center, middle

# In-situ underwater light measurements at the ice camp

---

# Vertical light profile measurements

- A total of 83 vertical light profiles were acquired

---

class: my-one-page-font, inverse, center, middle

# 3D Monte Carlo numerical simulations of radiative transfer

---

# The geometry

Fig. 1

Fig. 2


---

class: my-one-page-font, inverse, center, middle

# Main results

---

# Simulated underice light

Light regime (downard + upward) under ice.

Fig. 6+

---

class: my-one-page-font, inverse, center, middle

# Take home messages

- (KLu), which is up to two times less influenced by a heterogeneous incident light field than Kd in the vicinity of a melt pond, can be used as a proxy to estimate Ed(z) in the water column.

---

# Questions?

Massicotte P, Bécu G, Lambert-Girard S, Leymarie E, Babin M. Estimating Underwater Light Regime under Spatially Heterogeneous Sea Ice in the Arctic. Applied Sciences. 2018; 8(12):2693.
