---
title: "Estimating Underwater Light Regime under Spatially Heterogeneous Sea Ice in the Arctic"
subtitle: "GreenEdge Legacy meeting"
author: "P. Massicotte, G. Bécu, S. Lambert-Girard, E. Leymarie and M. Babin"
date: "2019-11-06 (Nice)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [xaringan-themer.css, styles.css]
    self_contained: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
editor_options:
  chunk_output_type: console
---

  <style type="text/css">
.remark-slide-content {
    font-size: 35px;
    padding: 1em 4em 1em 4em;
}
.remark-inline-code {
    font-size: 0.75em;
}

.verticalhorizontal {
    text-align:center;
 display:block;
}

.my-one-page-font > h1 {
  font-size: 120px;
}

strong {
    font-weight: normal;
}

</style>

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  out.width = "100%",
  fig.align = "center",
  fig.width = 8,
  fig.asp = 0.618, # 1 / phi
  fig.show = "hold",
  dev = "svg",
  message = FALSE,
  warning = FALSE,
  echo = FALSE
)

library(tidyverse)
library(ggpmthemes)
library(fontawesome)
library(knitr)
library(kableExtra)

theme_set(theme_exo(base_size = 12))
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
duo(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css",
  text_font_google = google_font("Questrial"),
  inverse_background_color = "#456A76",
  inverse_header_color = "#F5F5F5"
  # Yanone Kaffeesatz
)
```

# Outlines

1. File formats for data archiving.

2. Choosing the tools to read and manipulate your data.

3. Files and data organization.

4. Tidying and formatting data.

5. Backups.

6. Publishing your data.

7. Practical exercises with your data.

---

class: my-one-page-font, inverse, center, middle

# Lets keep in touch!

Presentation available here: http://tiny.cc/zxefez

`r fontawesome::fa("paper-plane", fill = "#d3ba68")` philippe.massicotte@takuvik.ulaval.ca
`r fontawesome::fa("link", fill = "#d3ba68")` www.pmassicotte.com
`r fontawesome::fa("twitter", fill = "#d3ba68")` @philmassicotte
`r fontawesome::fa("github", fill = "#d3ba68")` @pmassicotte

---

## sdf

This is a test...
